\documentclass[12pt,a4paper]{res}
\usepackage{a4-mancs}
\usepackage{pslatex}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{url}
\setlength\columnsep{40pt}
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{9.8in}
\setlength{\headsep}{0.2in}
\setlength{\headheight}{14.49998pt}
\setlength{\textheight}{297mm}
\renewcommand{\headrulewidth}{0pt}
\cfoot{}
\pagestyle{fancy}

\begin{document}
\thispagestyle{empty}
  \begin{center}
  \Large{Dragos Romario Rosu  \\ [12pt]}
  \normalsize 96 Jackson Crescent, Manchester, M15 5AA\\
  Mobile: 0774 340 7461, Email: rosudrag.dev@gmail.com\\
  Website: \url{http://rosudrag.github.io/}
  \end{center}
  
\begin{resume}
\vspace{-10mm}
\section{\large\bf Professional Experience}

\section{\bf 2015 - \textit{2016} \hspace{0.3mm} Code ComputerLove - Software Developer:}
\vspace{5mm}    
	\begin{itemize}
	\item[] Part of team of the year 2015 in Code, I've been a valuable asset for the company since day one. I've predominately worked on a .NET website project for the company's largest client.
	\item \textbf{Methodology:} Worked in an Agile, Lean environment with Scrum meetings, Kanban boards and TDD as development method. I've adapted easily to the numerous method changes we were experimenting with and got accustomed to trying new things on daily basis.
	\item \textbf{Continuous Integration:} Improved pipeline with Teamcity, Octopus and Jenkins by setting up new environments and hooking up to a statistics framework. Setup automatic acceptance tests in the build pipeline and also automated the umbraco database synchronisation, both upward and downwards on all environments.
	\item \textbf{KPI Dashboards:} Developed dashboards for our projects that provided us with visibility of any failures that might occur. By hooking up statistics to the dashboards I've generated a screen that could pinpoint fluctuations in profit to the software changes.
	\item \textbf{Main technologies:} .Net, C\#, Umbraco, ElasticSearch, Microsoft SQL, RabbitMQ, Dashing, NewRelic, Node, Ruby, ReddisDB
	\end{itemize}
	
\section{\bf 2013 - 2014 \hspace{0.5mm} Industrial Placement - CIVICA - Software Developer:}
\vspace{5mm}    
	\begin{itemize}
	\item[] Put in practice the techniques taught at University to quickly grasp the technologies the company used and made myself a real asset for the team.
	\item{\bf CIVICA best team nomination:} Came second place at best team awards in the company and I would like to think I played an important role in this.
	\item{\bf Skills and knowledge acquired:} C\# and OracleSQL and other specific Microsoft technologies: WCF, EntityFramework, ServiceBus, WPF, Scrum, Agile methodology, pair programming.
	\end{itemize}


\section{\large\bf Education}
\vspace{5mm}

\section{\bf 2011 - 2015 \hspace{1.5mm}The University of Manchester}
  
  \begin{itemize} % \item[] to prevent a bullet from appearing
     \item[] BSc (Hons) Computer Science  with Industrial Experience
     \item[] Degree result 2:1 \hspace{10mm}Overall results: 63\% 

     \item Developed an excellent IT foundation by combining the skills and knowledge taught at University with practical experience. Regularly worked in small size teams to plan, design and develop projects,   employing agile and pair programming techniques.
     \item Enhanced my algorithmic thinking through participation in challenging events and competitions.
     \item Progressed my ability to view a problem through different perspectives and the skill to combine them in order to produce a solution that will benefit all the involved parties.
   \end{itemize}

\newpage 

\section{\large\bf Achievements}
  \begin{itemize}
  \item {\bf Finalist HackManchester 2015} - \url{http://www.codecomputerlove.com/blog/2015/10/finalists-at-hack-manchester-2015/}
  \item {\bf NCC Group University challenge first prize} - penetration testing challenge.
  \end{itemize}

\section{\bf Manchester Ultimate Programming society:}
\vspace{5mm}    
    \begin{itemize}
    \item[] Conducted weekly presentations throughout the year and organised one 24 hour hackathon. I've managed to put my networking skills into practice to acquire sponsorship for prizes and catering.
    \item{\bf Most Innovative technical approach award:} Awarded at the "Open Source Hackathon" where I Teamed with a PhD student to create a project called "Group My contacts". My suggestion to using pair programming with the Cloud9 IDE had given us a velocity advantage which allowed us to merge multiple APIs that analysed and produced curious social groups through Facebook and Twitter contact analysis.

      \item {\bf Leadership:} Through hard work and dedication I worked my way up the hierarchy of the society and became the chairman of it. I managed to boost the events turnout and the attendance number had doubled by the end of the year.
     \end{itemize}

\section{\bf Notable university courses and themes:}
\vspace{2mm}
	\begin{itemize}		
	    \begin{multicols}{2}
		\item \vspace{-1.5mm} Advanced Algorithms
		\item \vspace{-1.5mm} Software Engineering and Patterns
		\item \vspace{-1.5mm} Computer Architecture
		\item \vspace{-1.5mm} Computer Networks
		\item \vspace{-1.5mm} Computer Graphics Image Processing
		\item \vspace{-1.5mm} Databases
		\item \vspace{-1.5mm} Human Computer Interaction
		\item \vspace{-1.5mm} Logic and Modeling, Verified Development
		\item \vspace{-1.5mm} Documents and the Web
		\item \vspace{-1.5mm} Distributed Systems and Mobile Systems
	    \end{multicols}
	\end{itemize}
	
\section{\large\bf Skills}
\vspace{2mm}
\section{IT}
\vspace{-1mm}
  \begin{itemize}

  \item[] {\bf Languages:} C\#, Python, Java, C, HTML, Assembly, OracleSQL, MySQL, Ruby, PHP.
  \item[] {\bf Applications and Frameworks:} .NET, Visual Studio, PyCharm, VSphere, Umbraco, ASP.NET MVC, IIS, Teamcity, Octopus, Jenkins, Redis, ElasticSearch, Azure, Amazon AWS, Heroku, Cloud9, Git, Automapper, AC3D, Latex, Office, Play Framework, Eclipse, Netbeans, VMWare, OpenGL.
  \item[] {\bf Servers \& Networking:} Experience in setting up windows / linux VM environments.
  \item[] {\bf Environments:} familiar with both UNIX and Windows operating systems where I've tackled different domains: virtualisation, caching, penetration testing, client-server architectures.
  \end{itemize}
\vspace{-3mm}
      
\section{\large\bf Voluntary work}
\vspace{5mm}
	\begin{itemize}
	\item[] I've been a PASS Leader and a Student Helper whilst at University: these activities shaped me into a better person, more empathetic and able to relate and help others with their issues.
	\end{itemize}
    
\section{Languages}
\vspace{-0.7mm}
\begin{itemize}
\item[] {\bf English:} IELTS 7.0
\item[] {\bf Romanian:} native.
\item[] {\bf French:} basic conversational level.
\end{itemize}
\vspace{-3mm}

\section{Driving}
\vspace{-0.7mm}
\begin{itemize}
\item[] Full clean driving licence.
\end{itemize}
  \vspace{-3mm}
  
\section{Hobbies}
\vspace{-0.7mm}
  \begin{itemize}
  \item[] Reading, swimming, dancing, gaming, skiing, traveling, exploring.
  \end{itemize}

\end{resume}
\end{document}